A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-02-15 manuscript.Rmd
summarise preparations for publishing
fix typo

<!--I am troubled by how we should recommend to learn git-->
Git is can be challenging to learn, because we are used to learn alone and Git is best learned with others.
We recommend to find a partner to attend an online lecture or workshop to learn the ins and outs of Git.

@@

We strongly suggest that you strive for respectful interactions with anyone who might want to contribute.
In fact, we hope it comes naturally to you.
To communicate that contributors can expect a welcoming and respectful environment, you can add the `r link( "https://www.contributor-covenant.org", "Contributor Covenant")` to your repository.
The Contributor Covenant is the code of conduct used by many open source project.
Contributing to an open project is daunting and a public pledge to value any contributions (even when you do not incorporate them) can help others to take the first step.

@@

>>>>

<!--I am troubled by how we should recommend to learn git-->
Git can be challenging to learn, because we are used to learn alone and Git is best learned with others.
We recommend to find a partner to attend an online lecture or workshop to learn the ins and outs of Git.

@@

We strongly suggest that you strive for respectful interactions with anyone who might want to contribute.
In fact, we hope it comes naturally to you.
To communicate that contributors can expect a welcoming and respectful environment, you can add the `r link( "https://www.contributor-covenant.org", "Contributor Covenant")` to your repository.
The Contributor Covenant is a code of conduct used by many open source project.
Contributing to an open project is daunting and a public pledge to value any contributions (even when you do not incorporate them) can help others to take the first step.

@@

If you have considered what you want to tell the public about the project with a readme, have chosen a license and thought about how to make collaboration welcoming, you may publish your Git repository.
